Brownian Dynein Model

### 2015-09-29 latex/derivation.tex
Slight change to derivation.tex.
Add work to derivation.tex.

Also by the law of cosines, we can see that:

\begin{equation}
   \Theta_{1} = \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})
\end{equation}

We use this to find the value of $X_{t}$ and $Y_{t}$:

@@

and

\begin{align}
  Y_{t} &= L_n\sin(\Theta_{1}) \\
        &=
\end{align}

This is getting ugly and complicated. I will not do it. I will do it when I need to. \\
\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{nb} &= 0 \\
  X_{nm} &= L_{s}*\cos(\Theta_{nb}) \\
  X_{t}  &= ?? \\
  X_{fm} &= L_{s}*\cos(\Theta_{fb}) \\
  X_{fb} &= L \\
\end{align}

>>>>

We can also use the law of cosines to find an expression for $\Theta_{1}$:

\begin{align}
   L_f^2 &= L^2 + L_n^2 - 2LL_n\cos(\Theta_{1}) \\
   \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
\end{align}

We use this to find the value of $X_{t}$:

@@

To find $Y_{t}$ we do something similar:

\begin{align}
  \Theta_{1} &= \cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n}) \\
  Y_{t} &= L_n\sin(\Theta_{1}) \\
       &= L_n\sin(\cos^{-1}(\frac{L^2+L_n^2-L_f^2}{2LL_n})) \\
       &= L_n\sqrt{1 - (\frac{L^2+L_n^2-L_f^2}{2LL_n})^2} \\
\end{align}

\section{Cartesian from Angular Coordinates}
This section lays out the definitions of the coordinates of the Dynein model. \\
\begin{align}
  X_{nb} &= 0 \\
  X_{nm} &= L_{s}*\cos(\Theta_{nb}) \\
  X_{t}  &= ?? \\
  X_{fm} &= L_{s}*\cos(\Theta_{fb}) \\
  X_{fb} &= L \\
\end{align}
